---
title: "V4_Creation of charts"
author: "Richard Alessi"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
global_start_time <- Sys.time()
library(dplyr)
library(ggplot2)
library(tibble)


library(tidyverse)
library(data.table)
```



## Read in values
```{r}
setwd("C:/Users/richa/Desktop/Thesis/Results")
scenarioNumber = "5a"
files_T5 = list.files(pattern = paste("Scenario", scenarioNumber,".*T5.*csv", sep = ""))

start_time =  Sys.time()
df_T5 = do.call(rbind, lapply(files_T5, fread))
end_time =  Sys.time()
print(end_time - start_time)
```

```{r}
df2_T5 = df_T5
df2_T5$Perc_A = df2_T5$Allocation_TreatmentA/df2_T5$Sample_size 
df2_T5$Perc_B = df2_T5$Allocation_TreatmentB/df2_T5$Sample_size 
df2_T5$Perc_C = df2_T5$Allocation_TreatmentC/df2_T5$Sample_size 
df2_T5$Perc_D = df2_T5$Allocation_TreatmentD/df2_T5$Sample_size 
df2_T5$Perc_E = df2_T5$Allocation_TreatmentE/df2_T5$Sample_size 
df2_T5$Power = 1*(df2_T5$ChiSq_pvalue<=0.05)
```


```{r}
# Models
NeymanModels = c("RA_Known_Neyman", "CARA_Known_Neyman", "RA_Estimated_Neyman", "CARA_Estimated_Neyman", "RA_DBCD_Neyman", "CARA_DBCD_Neyman")
RSIHRModels = c("RA_Known_RSIHR", "CARA_Known_RSIHR", "RA_Estimated_RSIHR", "CARA_Estimated_RSIHR", "RA_DBCD_RSIHR", "CARA_DBCD_RSIHR")
RosenbergerModels = c("RA_Known_Rosenberger", "CARA_Known_Rosenberger", "RA_Estimated_Rosenberger", "CARA_Estimated_Rosenberger", "RA_DBCD_Rosenberger", "CARA_DBCD_Rosenberger")
OAModels = c("RA_Known_OptimallyAdjusted", "CARA_Known_OptimallyAdjusted", "RA_Estimated_OptimallyAdjusted", "CARA_Estimated_OptimallyAdjusted", "RA_DBCD_OptimallyAdjusted", "CARA_DBCD_OptimallyAdjusted")
GittinsModels = c("RA_Gittins_FALSE","RA_Gittins_TRUE")
MLModels = c("RA_ML Model_Random", "RA_ML Model_PlayTheWinner", "RA_ML Model_PlayTheWinnerRandomised", "RA_ML Model_EpsilonGreedy", "RA_ML Model_SoftMax")
```



# Table 1 - Tables of key values
```{r}
n_s = unique(df2_T5$Sample_Size)
models = unique(df2_T5$Model)
df_summary_T5 = data.frame(Sample_size = integer(), Model = character() , averageSuccessProportion = numeric(), varianceSuccessProportion = numeric(), averageAllocatedA = numeric(), varianceAllocatedA = numeric(), averagePower= numeric() )

df_summary_T5 <- df2_T5 %>% group_by(Model, Sample_size) %>% summarise(averageSuccessProportion = mean(Successes_total/Sample_size), varSuccessProportion = var(Successes_total/Sample_size)
                                                                       , averageAllocatedA = mean(Perc_A/Sample_size), VarAllocatedA = var(Perc_A/Sample_size)
                                                                       , averageAllocatedB = mean(Perc_B/Sample_size), VarAllocatedB = var(Perc_B/Sample_size)
                                                                       , averageAllocatedC = mean(Perc_C/Sample_size), VarAllocatedC = var(Perc_C/Sample_size)
                                                                       , averageAllocatedD = mean(Perc_D/Sample_size), VarAllocatedD = var(Perc_D/Sample_size)
                                                                       , averageAllocatedE = mean(Perc_E/Sample_size), VarAllocatedE = var(Perc_E/Sample_size)
                         , Allocated_Max = max(mean(Perc_A/Sample_size), mean(Perc_B/Sample_size), mean(Perc_C/Sample_size), mean(Perc_D/Sample_size), mean(Perc_E/Sample_size))
                                                                       , averagePower = mean(Power), varPower = var(Power), ChiSq_005 = mean(ifelse(is.na(ChiSq_pvalue),1,ChiSq_pvalue) <= 0.05), ChiSq_001 = mean(ifelse(is.na(ChiSq_pvalue),1,ChiSq_pvalue) <= 0.01), LR_test_005 = mean(ifelse(is.na(LR_test_pvalue),1,LR_test_pvalue) <= 0.05), LR_test_001 = mean(ifelse(is.na(LR_test_pvalue),1,LR_test_pvalue) <= 0.01))

df_summary_T5
```


```{r}
df2_export_1 = df_summary_T5[df_summary_T5$Sample_size== 100,]
df2_export_2 = df_summary_T5[df_summary_T5$Sample_size == 1000,]
```

```{r}
df2_export_1 = select(df2_export_1, Model, P_Success = averageSuccessProportion, Allocated_Max, ChiSq = ChiSq_005, LR_test = LR_test_005)
df2_export_2 = select(df2_export_2, Model, P_Success = averageSuccessProportion, Allocated_Max, ChiSq = ChiSq_005, LR_test = LR_test_005)
print(xtable(df2_export_1, type = "latex"), file = paste("C:/Users/richa/Desktop/Thesis/Images/Tables/Table_1_n100_summary_Scenario",scenarioNumber,".tex", sep = ""))
print(xtable(df2_export_2, type = "latex"), file = paste("C:/Users/richa/Desktop/Thesis/Images/Tables/Table_2_n1000_summary_Scenario",scenarioNumber,".tex", sep = ""))
```


```{r}
df2_T5_Perc_A = df2_T5 %>% select(Model, Sample_size, Allocation_TreatmentA, Allocation_TreatmentB, Allocation_TreatmentC, Allocation_TreatmentD, Allocation_TreatmentE)
df_flat_T5 <- df2_T5_Perc_A %>% pivot_longer(cols = Allocation_TreatmentA:Allocation_TreatmentE, values_to = "mean") 

df2_T5$AvgSuccess = df2_T5$Successes_total/df2_T5$Sample_size
```





# Chart 1 - Stack bars of treatment allocations, t = 5, 

## A n = 100 || B n = 100
```{r}
plot_A <- ggplot(data = df_flat_T5[df_flat_T5$Sample_size == 100,], aes(x = Model, y = mean, fill = name), width = 2000) +  geom_bar(position="fill", stat="identity") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+xlab("Model") + ylab("Allocation breakdown")+ scale_y_continuous(labels = scales::percent)


plot_B <- ggplot(data = df_flat_T5[df_flat_T5$Sample_size == 1000,], aes(x = Model, y = mean, fill = name), width = 2000) +  geom_bar(position="fill", stat="identity") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+xlab("Model") + ylab("Allocation breakdown")+ scale_y_continuous(labels = scales::percent)

plot_grid(plot_A, plot_B, ncol = 1, align = 'hv', labels = c("A", "B"))

ggsave(paste("C:/Users/richa/Desktop/Thesis/Images/Scenario_",scenarioNumber,"/Chart1_Combined_stacks_PercA_n100_n1000_t5_",".pdf", sep = ""), device = "pdf", width = 40, height = 30, units = "cm")
```


# Chart 2 Violins by allocation method, n - 50, 1000
# n = 50 
```{r}
labelMin = floor(min(df2_T5$AvgSuccess[df2_T5$Sample_size == 50])*20)/20
labelMax = ceiling(max(df2_T5$AvgSuccess[df2_T5$Sample_size == 50])*20)/20
```


```{r}
plot_A <- ggplot(data = df2_T5[apply(bind_cols(df2_T5$Sample_size == 50, (df2_T5$Model %in% NeymanModels)), 1, all),], aes(Model, Successes_total/Sample_size), width = 200) + geom_violin(scale = "area") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+xlab("Model") + ylab("Total success proportion")+ scale_y_continuous(labels = scales::percent, limits = c(labelMin, labelMax))

plot_B <- ggplot(data = df2_T5[apply(bind_cols(df2_T5$Sample_size == 50, (df2_T5$Model %in% RSIHRModels)), 1, all),], aes(Model, Successes_total/Sample_size), width = 200) + geom_violin(scale = "area") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+xlab("Model") + ylab("Total success proportion")+ scale_y_continuous(labels = scales::percent, limits = c(labelMin, labelMax))

plot_C <- ggplot(data = df2_T5[apply(bind_cols(df2_T5$Sample_size == 50, (df2_T5$Model %in% RosenbergerModels)), 1, all),], aes(Model, Successes_total/Sample_size), width = 200) + geom_violin(scale = "area") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+xlab("Model") + ylab("Total success proportion")+ scale_y_continuous(labels = scales::percent, limits = c(labelMin, labelMax))

plot_D <- ggplot(data = df2_T5[apply(bind_cols(df2_T5$Sample_size == 50, (df2_T5$Model %in% OAModels)), 1, all),], aes(Model, Successes_total/Sample_size), width = 200) + geom_violin(scale = "area") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+xlab("Model") + ylab("Total success proportion")+ scale_y_continuous(labels = scales::percent, limits = c(labelMin, labelMax))

plot_E <- ggplot(data = df2_T5[apply(bind_cols(df2_T5$Sample_size == 50, (df2_T5$Model %in% GittinsModels)), 1, all),], aes(Model, Successes_total/Sample_size), width = 200) + geom_violin(scale = "area") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+xlab("Model") + ylab("Total success proportion")+ scale_y_continuous(labels = scales::percent, limits = c(labelMin, labelMax))

plot_F <- ggplot(data = df2_T5[apply(bind_cols(df2_T5$Sample_size == 50, (df2_T5$Model %in% MLModels)), 1, all),], aes(Model, Successes_total/Sample_size), width = 200) + geom_violin(scale = "area") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+xlab("Model") + ylab("Total success proportion")+ scale_y_continuous(labels = scales::percent, limits = c(labelMin, labelMax))

plot_grid(plot_A, plot_B, plot_C, plot_D, plot_E, plot_F, ncol = 2, align = 'hv', labels = c("A", "B", "C", "D", "E", "F"))

ggsave(paste("C:/Users/richa/Desktop/Thesis/Images/Scenario_",scenarioNumber,"/Chart2_1_Combined_violins_SuccessComparison_n50_T5_Scenario_",scenarioNumber,".pdf", sep = ""), device = "pdf", width = 40, height = 50, units = "cm")
```

# n = 1000
```{r}
labelMin = floor(min(df2_T5$AvgSuccess[df2_T5$Sample_size == 1000])*20)/20
labelMax = ceiling(max(df2_T5$AvgSuccess[df2_T5$Sample_size == 1000])*20)/20
```

```{r}
plot_A <- ggplot(data = df2_T5[apply(bind_cols(df2_T5$Sample_size == 1000, (df2_T5$Model %in% NeymanModels)), 1, all),], aes(Model, Successes_total/Sample_size), width = 200) + geom_violin(scale = "area") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+xlab("Model") + ylab("Total success proportion")+ scale_y_continuous(labels = scales::percent, limits = c(labelMin, labelMax))

plot_B <- ggplot(data = df2_T5[apply(bind_cols(df2_T5$Sample_size == 1000, (df2_T5$Model %in% RSIHRModels)), 1, all),], aes(Model, Successes_total/Sample_size), width = 200) + geom_violin(scale = "area") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+xlab("Model") + ylab("Total success proportion")+ scale_y_continuous(labels = scales::percent, limits = c(labelMin, labelMax))

plot_C <- ggplot(data = df2_T5[apply(bind_cols(df2_T5$Sample_size == 1000, (df2_T5$Model %in% RosenbergerModels)), 1, all),], aes(Model, Successes_total/Sample_size), width = 200) + geom_violin(scale = "area") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+xlab("Model") + ylab("Total success proportion")+ scale_y_continuous(labels = scales::percent, limits = c(labelMin, labelMax))

plot_D <- ggplot(data = df2_T5[apply(bind_cols(df2_T5$Sample_size == 1000, (df2_T5$Model %in% OAModels)), 1, all),], aes(Model, Successes_total/Sample_size), width = 200) + geom_violin(scale = "area") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+xlab("Model") + ylab("Total success proportion")+ scale_y_continuous(labels = scales::percent, limits = c(labelMin, labelMax))

plot_E <- ggplot(data = df2_T5[apply(bind_cols(df2_T5$Sample_size == 1000, (df2_T5$Model %in% GittinsModels)), 1, all),], aes(Model, Successes_total/Sample_size), width = 200) + geom_violin(scale = "area") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+xlab("Model") + ylab("Total success proportion")+ scale_y_continuous(labels = scales::percent, limits = c(labelMin, labelMax))

plot_F <- ggplot(data = df2_T5[apply(bind_cols(df2_T5$Sample_size == 1000, (df2_T5$Model %in% MLModels)), 1, all),], aes(Model, Successes_total/Sample_size), width = 200) + geom_violin(scale = "area") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+xlab("Model") + ylab("Total success proportion")+ scale_y_continuous(labels = scales::percent, limits = c(labelMin, labelMax))

plot_grid(plot_A, plot_B, plot_C, plot_D, plot_E, plot_F, ncol = 2, align = 'hv', labels = c("A", "B", "C", "D", "E", "F"))

ggsave(paste("C:/Users/richa/Desktop/Thesis/Images/Scenario_",scenarioNumber,"/Chart2_1_Combined_violins_SuccessComparison_n1000_T5_Scenario_",scenarioNumber,".pdf", sep = ""), device = "pdf", width = 40, height = 50, units = "cm")
```


# Chart 3 - Average success proportion with sample size - T = 5
```{r}
labelMin = floor(min(df_summary_T5$averageSuccessProportion)*20)/20
labelMax = ceiling(max(df_summary_T5$averageSuccessProportion)*20)/20
```

```{r}
plot_A <- ggplot(data = df_summary_T5[df_summary_T5$Model %in% NeymanModels,], aes(Sample_size, averageSuccessProportion, color = Model)) +geom_line()+xlab("Sample size") + ylab("Total success proprtion average")+ scale_y_continuous(labels = scales::percent, limits = c(labelMin, labelMax))

plot_B <-  ggplot(data = df_summary_T5[df_summary_T5$Model %in% RSIHRModels,], aes(Sample_size, averageSuccessProportion, color = Model)) +geom_line()+xlab("Sample size") + ylab("Total success proprtion average")+ scale_y_continuous(labels = scales::percent, limits = c(labelMin, labelMax))

plot_C <- ggplot(data = df_summary_T5[df_summary_T5$Model %in% RosenbergerModels,], aes(Sample_size, averageSuccessProportion, color = Model)) +geom_line()+xlab("Sample size") + ylab("Total success proprtion average")+ scale_y_continuous(labels = scales::percent, limits = c(labelMin, labelMax))

plot_D <- ggplot(data = df_summary_T5[df_summary_T5$Model %in% OAModels,], aes(Sample_size, averageSuccessProportion, color = Model)) +geom_line()+xlab("Sample size") + ylab("Total success proprtion average")+ scale_y_continuous(labels = scales::percent, limits = c(labelMin, labelMax))

plot_E <- ggplot(data = df_summary_T5[df_summary_T5$Model %in% GittinsModels,], aes(Sample_size, averageSuccessProportion, color = Model)) +geom_line()+xlab("Sample size") + ylab("Total success proprtion average")+ scale_y_continuous(labels = scales::percent, limits = c(labelMin, labelMax))

plot_F <- ggplot(data = df_summary_T5[df_summary_T5$Model %in% MLModels,], aes(Sample_size, averageSuccessProportion, color = Model)) +geom_line()+xlab("Sample size") + ylab("Total success proprtion average")+ scale_y_continuous(labels = scales::percent, limits = c(labelMin, labelMax))

plot_grid(plot_A, plot_B, plot_C, plot_D, plot_E, plot_F, ncol = 2, align = 'hv', labels = c("A", "B", "C", "D", "E", "F"))

ggsave(paste("C:/Users/richa/Desktop/Thesis/Images/Scenario_",scenarioNumber,"/Chart3_Combined_line_avgSuccessProp_T5_Scenario_",scenarioNumber,".pdf", sep = ""), device = "pdf", width = 40, height = 30, units = "cm")
```



# Chart 5 Chi Sq power with sample size

```{r}
ylabels = c("Power of Chi-Squared test (5% LoS)",
            "Power of Chi-Squared test (5% LoS)",
            "Type 1 error rate",
            "Power of Chi-Squared test (5% LoS)",
            "Type 1 error rate"
            )
ylabel = ylabels[as.numeric(substr(scenarioNumber,1,1))]
```


```{r}
labelMin = floor(min(df_summary_T5$ChiSq_005)*20)/20
labelMax = ceiling(max(df_summary_T5$ChiSq_005)*20)/20
```

```{r}
plot_A <- ggplot(data = df_summary_T5[df_summary_T5$Model %in% NeymanModels,], aes(Sample_size, ChiSq_005, color = Model)) +geom_line()+xlab("Sample size") + ylab(ylabel)+ scale_y_continuous(labels = scales::percent, limits = c(labelMin, labelMax))

plot_B <- ggplot(data = df_summary_T5[df_summary_T5$Model %in% RSIHRModels,], aes(Sample_size, ChiSq_005, color = Model)) +geom_line()+xlab("Sample size") + ylab(ylabel)+ scale_y_continuous(labels = scales::percent, limits = c(labelMin, labelMax))

plot_C <- ggplot(data = df_summary_T5[df_summary_T5$Model %in% RosenbergerModels,], aes(Sample_size, ChiSq_005, color = Model)) +geom_line()+xlab("Sample size") + ylab(ylabel)+ scale_y_continuous(labels = scales::percent, limits = c(labelMin, labelMax))

plot_D <- ggplot(data = df_summary_T5[df_summary_T5$Model %in% OAModels,], aes(Sample_size, ChiSq_005, color = Model)) +geom_line()+xlab("Sample size") + ylab(ylabel)+ scale_y_continuous(labels = scales::percent, limits = c(labelMin, labelMax))

plot_E <- ggplot(data = df_summary_T5[df_summary_T5$Model %in% GittinsModels,], aes(Sample_size, ChiSq_005, color = Model)) +geom_line()+xlab("Sample size") + ylab(ylabel)+ scale_y_continuous(labels = scales::percent, limits = c(labelMin, labelMax))

plot_F <- ggplot(data = df_summary_T5[df_summary_T5$Model %in% MLModels,], aes(Sample_size, ChiSq_005, color = Model)) +geom_line()+xlab("Sample size") + ylab(ylabel)+ scale_y_continuous(labels = scales::percent, limits = c(labelMin, labelMax))

plot_grid(plot_A, plot_B, plot_C, plot_D, plot_E, plot_F, ncol = 2, align = 'hv', labels = c("A", "B", "C", "D", "E", "F"))

ggsave(paste("C:/Users/richa/Desktop/Thesis/Images/Scenario_",scenarioNumber,"/Chart5_1_Combined_ChiSq_power_005_t5_Scenario_",scenarioNumber,".pdf", sep = ""), device = "pdf", width = 40, height = 30, units = "cm")
```

## 2. Alpha = 0.01
```{r}
ylabels = c("Power of Chi-Squared test (1% LoS)",
            "Power of Chi-Squared test (1% LoS)",
            "Type 1 error rate",
            "Power of Chi-Squared test (1% LoS)",
            "Type 1 error rate"
            )
ylabel = ylabels[as.numeric(substr(scenarioNumber,1,1))]
```


```{r}
labelMin = floor(min(df_summary_T5$ChiSq_001)*20)/20
labelMax = ceiling(max(df_summary_T5$ChiSq_001)*20)/20
```

```{r}
plot_A <- ggplot(data = df_summary_T5[df_summary_T5$Model %in% NeymanModels,], aes(Sample_size, ChiSq_001, color = Model)) +geom_line()+xlab("Sample size") + ylab(ylabel)+ scale_y_continuous(labels = scales::percent, limits = c(labelMin, labelMax))

plot_A <- ggplot(data = df_summary_T5[df_summary_T5$Model %in% RSIHRModels,], aes(Sample_size, ChiSq_001, color = Model)) +geom_line()+xlab("Sample size") + ylab(ylabel)+ scale_y_continuous(labels = scales::percent, limits = c(labelMin, labelMax))

plot_A <- ggplot(data = df_summary_T5[df_summary_T5$Model %in% RosenbergerModels,], aes(Sample_size, ChiSq_001, color = Model)) +geom_line()+xlab("Sample size") + ylab(ylabel)+ scale_y_continuous(labels = scales::percent, limits = c(labelMin, labelMax))

plot_A <- ggplot(data = df_summary_T5[df_summary_T5$Model %in% OAModels,], aes(Sample_size, ChiSq_001, color = Model)) +geom_line()+xlab("Sample size") + ylab(ylabel)+ scale_y_continuous(labels = scales::percent, limits = c(labelMin, labelMax))

plot_A <- ggplot(data = df_summary_T5[df_summary_T5$Model %in% GittinsModels,], aes(Sample_size, ChiSq_001, color = Model)) +geom_line()+xlab("Sample size") + ylab(ylabel)+ scale_y_continuous(labels = scales::percent, limits = c(labelMin, labelMax))

plot_A <- ggplot(data = df_summary_T5[df_summary_T5$Model %in% MLModels,], aes(Sample_size, ChiSq_001, color = Model)) +geom_line()+xlab("Sample size") + ylab(ylabel)+ scale_y_continuous(labels = scales::percent, limits = c(labelMin, labelMax))

plot_grid(plot_A, plot_B, plot_C, plot_D, plot_E, plot_F, ncol = 2, align = 'hv', labels = c("A", "B", "C", "D", "E", "F"))

ggsave(paste("C:/Users/richa/Desktop/Thesis/Images/Scenario_",scenarioNumber,"/Chart5_2_Combined_ChiSq_power_001_t5_Scenario_",scenarioNumber,".pdf", sep = ""), device = "pdf", width = 40, height = 30, units = "cm")
```


# Chart 5 Chi Sq power with sample size
```{r}
ylabels = c("Power of Likelihood ratio test (5% LoS)",
            "Power of Likelihood ratio test (5% LoS)",
            "Power of Likelihood ratio test (5% LoS)",
            "Power of Likelihood ratio test (5% LoS)",
            "Type 1 error rate"
            )

ylabel = ylabels[as.numeric(substr(scenarioNumber,1,1))]
```

## 1. Alpha = 0.05
```{r}
labelMin = floor(min(df_summary_T5$LR_test_005)*20)/20
labelMax = ceiling(max(df_summary_T5$LR_test_005)*20)/20
```

```{r}
plot_A <- ggplot(data = df_summary_T5[df_summary_T5$Model %in% NeymanModels,], aes(Sample_size, LR_test_005, color = Model)) +geom_line()+xlab("Sample size") + ylab(ylabel)+ scale_y_continuous(labels = scales::percent, limits = c(labelMin, labelMax))

plot_B <- ggplot(data = df_summary_T5[df_summary_T5$Model %in% RSIHRModels,], aes(Sample_size, LR_test_005, color = Model)) +geom_line()+xlab("Sample size") + ylab(ylabel)+ scale_y_continuous(labels = scales::percent, limits = c(labelMin, labelMax))

plot_C <- ggplot(data = df_summary_T5[df_summary_T5$Model %in% RosenbergerModels,], aes(Sample_size, LR_test_005, color = Model)) +geom_line()+xlab("Sample size") + ylab(ylabel)+ scale_y_continuous(labels = scales::percent, limits = c(labelMin, labelMax))

plot_D <- ggplot(data = df_summary_T5[df_summary_T5$Model %in% OAModels,], aes(Sample_size, LR_test_005, color = Model)) +geom_line()+xlab("Sample size") + ylab(ylabel)+ scale_y_continuous(labels = scales::percent, limits = c(labelMin, labelMax))

plot_E <- ggplot(data = df_summary_T5[df_summary_T5$Model %in% GittinsModels,], aes(Sample_size, LR_test_005, color = Model)) +geom_line()+xlab("Sample size") + ylab(ylabel)+ scale_y_continuous(labels = scales::percent, limits = c(labelMin, labelMax))

plot_F <- ggplot(data = df_summary_T5[df_summary_T5$Model %in% MLModels,], aes(Sample_size, LR_test_005, color = Model)) +geom_line()+xlab("Sample size") + ylab(ylabel)+ scale_y_continuous(labels = scales::percent, limits = c(labelMin, labelMax))

plot_grid(plot_A, plot_B, plot_C, plot_D, plot_E, plot_F, ncol = 2, align = 'hv', labels = c("A", "B", "C", "D", "E", "F"))

ggsave(paste("C:/Users/richa/Desktop/Thesis/Images/Scenario_",scenarioNumber,"/Chart5_1_Combined_LR_test_power_005_t5_Scenario_",scenarioNumber,".pdf", sep = ""), device = "pdf", width = 40, height = 30, units = "cm")
```


## 2. Alpha = 0.01
```{r}
ylabels = c("Power of Likelihood ratio test (1% LoS)",
            "Power of Likelihood ratio test (1% LoS)",
            "Power of Likelihood ratio test (1% LoS)",
            "Power of Likelihood ratio test (1% LoS)",
            "Type 1 error rate"
            )

ylabel = ylabels[as.numeric(substr(scenarioNumber,1,1))]
```

```{r}
labelMin = floor(min(df_summary_T5$LR_test_001)*20)/20
labelMax = ceiling(max(df_summary_T5$LR_test_001)*20)/20
```


```{r}
plot_A <- ggplot(data = df_summary_T5[df_summary_T5$Model %in% NeymanModels,], aes(Sample_size, LR_test_001, color = Model)) +geom_line()+xlab("Sample size") + ylab(ylabel)+ scale_y_continuous(labels = scales::percent, limits = c(labelMin, labelMax))

plot_B <- ggplot(data = df_summary_T5[df_summary_T5$Model %in% RSIHRModels,], aes(Sample_size, LR_test_001, color = Model)) +geom_line()+xlab("Sample size") + ylab(ylabel)+ scale_y_continuous(labels = scales::percent, limits = c(labelMin, labelMax))

plot_C <- ggplot(data = df_summary_T5[df_summary_T5$Model %in% RosenbergerModels,], aes(Sample_size, LR_test_001, color = Model)) +geom_line()+xlab("Sample size") + ylab(ylabel)+ scale_y_continuous(labels = scales::percent, limits = c(labelMin, labelMax))

plot_D <- ggplot(data = df_summary_T5[df_summary_T5$Model %in% OAModels,], aes(Sample_size, LR_test_001, color = Model)) +geom_line()+xlab("Sample size") + ylab(ylabel)+ scale_y_continuous(labels = scales::percent, limits = c(labelMin, labelMax))

plot_E <- ggplot(data = df_summary_T5[df_summary_T5$Model %in% GittinsModels,], aes(Sample_size, LR_test_001, color = Model)) +geom_line()+xlab("Sample size") + ylab(ylabel)+ scale_y_continuous(labels = scales::percent, limits = c(labelMin, labelMax))

plot_F <- ggplot(data = df_summary_T5[df_summary_T5$Model %in% MLModels,], aes(Sample_size, LR_test_001, color = Model)) +geom_line()+xlab("Sample size") + ylab(ylabel)+ scale_y_continuous(labels = scales::percent, limits = c(labelMin, labelMax))

plot_grid(plot_A, plot_B, plot_C, plot_D, plot_E, plot_F, ncol = 2, align = 'hv', labels = c("A", "B", "C", "D", "E", "F"))

ggsave(paste("C:/Users/richa/Desktop/Thesis/Images/Scenario_",scenarioNumber,"/Chart5_2_Combined_LR_test_power_001_t5_Scenario_",scenarioNumber,".pdf", sep = ""), device = "pdf", width = 40, height = 30, units = "cm")
```

# Chart 7 Scatter of power and average success
```{r}
ylabels = c("Power of Chi-Squared test (5% LoS)",
            "Power of Chi-Squared test (5% LoS)",
            "Type 1 error rate",
            "Power of Chi-Squared test (5% LoS)",
            "Type 1 error rate"
            )
ylabel = ylabels[as.numeric(substr(scenarioNumber,1,1))]
```

```{r}
xlabelMin = floor(min(df_summary_T5$averageSuccessProportion)*20)/20
xlabelMax = ceiling(max(df_summary_T5$averageSuccessProportion)*20)/20

ylabelMin = floor(min(df_summary_T5$ChiSq_005)*20)/20
ylabelMax = ceiling(max(df_summary_T5$ChiSq_005)*20)/20
```



## n = 30, 100
```{r}
plot_A <- ggplot(data = df_summary_T5[df_summary_T5$Sample_size == 30,], aes(x = averageSuccessProportion , y = ChiSq_005, color = Model, label = Model), width = 200) + geom_point() +xlab("Average total successes") + ylab(ylabel)+ scale_y_continuous(labels = scales::percent, limits = c(ylabelMin, ylabelMax)) + scale_x_continuous(labels = scales::percent, limits = c(xlabelMin, xlabelMax)) + theme(legend.position = "none")

plot_B <- ggplot(data = df_summary_T5[df_summary_T5$Sample_size == 100,], aes(x = averageSuccessProportion , y = ChiSq_005, color = Model), width = 200) + geom_point() +xlab("Average total successes") + ylab(ylabel)+ scale_y_continuous(labels = scales::percent, limits = c(ylabelMin, ylabelMax)) + scale_x_continuous(labels = scales::percent, limits = c(xlabelMin, xlabelMax)) + theme(legend.position = "none")

plot_grid(plot_A, plot_B, ncol = 1, align = 'hv', labels = c("A", "B"))


ggsave(paste("C:/Users/richa/Desktop/Thesis/Images/Scenario_",scenarioNumber,"/Chart7_Combined_Scatter_Power_Success_n30_n100_t5_Scenario_",scenarioNumber,".pdf", sep = ""), device = "pdf", width = 20, height = 20, units = "cm")
```


# Chart 9 - Change in variance of total successes proportion with sample size - T = 2
```{r}
labelMin = floor(min(df_summary_T5$varSuccessProportion)*200)/200
labelMax = ceiling(max(df_summary_T5$varSuccessProportion)*200)/200
```

```{r}
ggplot(data =  df_summary_T5, aes(Sample_size, varSuccessProportion, color = Model)) +geom_line()+xlab("Sample size") + ylab("Variance of success proportion") + theme(legend.position="bottom") + theme(legend.position = "none")  + ylim(labelMin, labelMax)
ggsave(paste("C:/Users/richa/Desktop/Thesis/Images/Scenario_",scenarioNumber,"/Chart9_all_line_varSuccessProp_t5_Scenario_",scenarioNumber,".pdf", sep = ""), device = "pdf", width = 15, units = "cm")
```

```{r}
plot_A <- ggplot(data =  df_summary_T5[(df_summary_T5$Model %in% NeymanModels),], aes(Sample_size, varSuccessProportion, color = Model)) +geom_line()+xlab("Sample size") + ylab("Variance of success proportion") + theme(legend.position="bottom")+ xlim(0, 1000) + ylim(labelMin, labelMax)

plot_B <- ggplot(data =  df_summary_T5[(df_summary_T5$Model %in% RSIHRModels),], aes(Sample_size, varSuccessProportion, color = Model)) +geom_line()+xlab("Sample size") + ylab("Variance of success proportion") + theme(legend.position="bottom")+ xlim(0, 1000) + ylim(labelMin, labelMax)

plot_C <- ggplot(data =  df_summary_T5[(df_summary_T5$Model %in% RosenbergerModels),], aes(Sample_size, varSuccessProportion, color = Model)) +geom_line()+xlab("Sample size") + ylab("Variance of success proportion") + theme(legend.position="bottom")+ xlim(0, 1000) + ylim(labelMin, labelMax)

plot_D <- ggplot(data =  df_summary_T5[(df_summary_T5$Model %in% OAModels),], aes(Sample_size, varSuccessProportion, color = Model)) +geom_line()+xlab("Sample size") + ylab("Variance of success proportion") + theme(legend.position="bottom")+ xlim(0, 1000) + ylim(labelMin, labelMax)

plot_E <- ggplot(data =  df_summary_T5[(df_summary_T5$Model %in% GittinsModels),], aes(Sample_size, varSuccessProportion, color = Model)) +geom_line()+xlab("Sample size") + ylab("Variance of success proportion") + theme(legend.position="bottom")+ xlim(0, 1000) + ylim(labelMin, labelMax)

plot_F <- ggplot(data =  df_summary_T5[(df_summary_T5$Model %in% MLModels),], aes(Sample_size, varSuccessProportion, color = Model)) +geom_line()+xlab("Sample size") + ylab("Variance of success proportion") + theme(legend.position="bottom")+ xlim(0, 1000)

plot_grid(plot_A, plot_B, plot_C, plot_D, plot_E, plot_F, ncol = 2, align = 'hv', labels = c("A", "B", "C", "D", "E", "F"))

ggsave(paste("C:/Users/richa/Desktop/Thesis/Images/Scenario_",scenarioNumber,"/Chart9_Combined_line_varSuccessProp_t5_Scenario_",scenarioNumber,".pdf", sep = ""), device = "pdf", width = 40, height = 30, units = "cm")
```




```{r}
global_end_time <- Sys.time()
print(global_end_time - global_start_time)
```

