---
title: "V4_Creation of charts"
author: "Richard Alessi"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(dplyr)
library(ggplot2)
library(tibble)
library(xtable)
library(cowplot)
library(tidyverse)
library(data.table)
```



## Read in values
```{r}
setwd("C:/Users/richa/Desktop/Thesis/Results")
scenarioNumber = "5"
files_T2 = list.files(pattern = paste("Scenario", scenarioNumber,".*T2.*csv", sep = ""))
files_T2_RPTW = files_T2[grepl("RPTW", files_T2, fixed = TRUE)]
files_T2 = files_T2[!grepl("RPTW", files_T2, fixed = TRUE)]
```

```{r}
setwd("C:/Users/richa/Desktop/Thesis/Results")
start_time =  Sys.time()
df_T2 = do.call(rbind, lapply(files_T2, fread))
end_time =  Sys.time()
print(end_time - start_time)

df2_T2 = df_T2[df_T2$Model != "RA_ML Model_PlayTheWinnerRandomised", ]

df_RPTW = do.call(rbind, lapply(files_T2_RPTW, fread))
df2_T2 = rbind(df2_T2, df_RPTW)
```

```{r}
df2_T2$Perc_A = df2_T2$Allocation_TreatmentA/df2_T2$Sample_size 
df2_T2$AvgSuccess = df2_T2$Successes_total/df2_T2$Sample_size
df2_T2$Power = 1*(df2_T2$ChiSq_pvalue<=0.05)
```

```{r}
# Models
NeymanModels = c("RA_Known_Neyman", "CARA_Known_Neyman", "RA_Estimated_Neyman", "CARA_Estimated_Neyman", "RA_DBCD_Neyman", "CARA_DBCD_Neyman")
RSIHRModels = c("RA_Known_RSIHR", "CARA_Known_RSIHR", "RA_Estimated_RSIHR", "CARA_Estimated_RSIHR", "RA_DBCD_RSIHR", "CARA_DBCD_RSIHR")
RosenbergerModels = c("RA_Known_Rosenberger", "CARA_Known_Rosenberger", "RA_Estimated_Rosenberger", "CARA_Estimated_Rosenberger", "RA_DBCD_Rosenberger", "CARA_DBCD_Rosenberger")
OAModels = c("RA_Known_OptimallyAdjusted", "CARA_Known_OptimallyAdjusted", "RA_Estimated_OptimallyAdjusted", "CARA_Estimated_OptimallyAdjusted", "RA_DBCD_OptimallyAdjusted", "CARA_DBCD_OptimallyAdjusted")
GittinsModels = c("RA_Gittins_FALSE","RA_Gittins_TRUE")
MLModels = c("RA_ML Model_Random", "RA_ML Model_PlayTheWinner", "RA_ML Model_PlayTheWinnerRandomised", "RA_ML Model_EpsilonGreedy", "RA_ML Model_SoftMax")
```




# Table 1 - Tables of key values
```{r}
n_s = unique(df2_T2$Sample_Size)
models = unique(df2_T2$Model)

df_summary_T2 <- df2_T2 %>% group_by(Model, Sample_size) %>% summarise(averageSuccessProportion = mean(Successes_total/Sample_size), varSuccessProportion = var(Successes_total/Sample_size), averageAllocatedA = mean(Perc_A), VarAllocatedA = var(Perc_A), averagePower = mean(Power), varPower = var(Power), Z0_avg_all_A = mean(Z0_Allocation_TreatmentA/Sample_size), Z0_avg_successes_A = mean(Z0_Successes_TreatmentA/Sample_size), Z0_avg_successes_B = mean(Z0_Successes_TreatmentB/Sample_size), ChiSq_005 = mean(ifelse(is.na(ChiSq_pvalue),1,ChiSq_pvalue) <= 0.05), ChiSq_001 = mean(ifelse(is.na(ChiSq_pvalue),1,ChiSq_pvalue) <= 0.01), LR_test_005 = mean(ifelse(is.na(LR_test_pvalue),1,LR_test_pvalue) <= 0.05), LR_test_001 = mean(ifelse(is.na(LR_test_pvalue),1,LR_test_pvalue) <= 0.01), observations = n())

df2_export_1 = df_summary_T2[df_summary_T2$Sample_size== 100,]
df2_export_2 = df_summary_T2[df_summary_T2$Sample_size == 1000,]
```

```{r}
df2_export_1 = select(df2_export_1, Model, P_Success = averageSuccessProportion, Allocated_A = averageAllocatedA, ChiSq = ChiSq_005, LR_test = LR_test_005)
df2_export_2 = select(df2_export_2, Model, P_Success = averageSuccessProportion, Allocated_A = averageAllocatedA, ChiSq = ChiSq_005, LR_test = LR_test_005)
print(xtable(df2_export_1, type = "latex"), file = paste("C:/Users/richa/Desktop/Thesis/Images/Tables/Table_1_n100_summary_Scenario",scenarioNumber,".tex", sep = ""))
print(xtable(df2_export_2, type = "latex"), file = paste("C:/Users/richa/Desktop/Thesis/Images/Tables/Table_2_n1000_summary_Scenario",scenarioNumber,".tex", sep = ""))
```


# Chart 1.1 - Percent allocated to A, all model violins, t = 2, n = 100, 1000
```{r}
plot_A <- ggplot(data = df2_T2[df2_T2$Sample_size == 100,], aes(Model, Perc_A), width = 500) + geom_violin(scale = "area") +xlab("Model") + ylab("% allocated to treatment A")+ scale_y_continuous(labels = scales::percent, limits = c(0,1))+theme_bw(base_size = 20)+ theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

plot_B <- ggplot(data = df2_T2[df2_T2$Sample_size == 1000,], aes(Model, Perc_A), width = 500) + geom_violin(scale = "area") +xlab("Model") + ylab("% allocated to treatment A")+ scale_y_continuous(labels = scales::percent, limits = c(0,1))+theme_bw(base_size = 20)+ theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

plot_grid(plot_A, plot_B, labels = c('A', 'B'), ncol = 1, align = 'hv')

ggsave(paste("C:/Users/richa/Desktop/Thesis/Images/Scenario_",scenarioNumber,"/Chart1_1_Combined_violins_percA_n1000_t2_Scenario_",scenarioNumber,".pdf", sep = ""), device = "pdf", height = 50, width = 50, units = "cm")
```


# Chart 1.2 - Total successes, all model violins, t = 2, n = 100, 1000
```{r}
plot_A <- ggplot(data = df2_T2[df2_T2$Sample_size == 100,], aes(Model, Successes_total/Sample_size), width = 500) + geom_violin(scale = "area") +theme_bw(base_size = 20)+ theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+xlab("Model") + ylab("Average success proportion")+ scale_y_continuous(labels = scales::percent, limits = c(0,1))

plot_B <- ggplot(data = df2_T2[df2_T2$Sample_size == 1000,], aes(Model, Successes_total/Sample_size), width = 500) + geom_violin(scale = "area") +theme_bw(base_size = 20)+ theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+xlab("Model") + ylab("Average success proportion")+ scale_y_continuous(labels = scales::percent, limits = c(0,1))

plot_grid(plot_A, plot_B, labels = c('A', 'B'), ncol = 1, align = 'hv')
ggsave(paste("C:/Users/richa/Desktop/Thesis/Images/Scenario_",scenarioNumber,"/Chart1_2_Combined_violins_success_n1000_t2_Scenario_",scenarioNumber,".pdf", sep = ""), device = "pdf", width = 30, height = 30, units = "cm")
```


# Chart 2 Violins by allocation method, n - 50, 1000
```{r}
plot_A <- ggplot(data = df2_T2[apply(bind_cols(df2_T2$Sample_size == 50, (df2_T2$Model %in% NeymanModels)), 1, all),], aes(Model, Successes_total/Sample_size), width = 200, height = 200) + geom_violin(scale = "area") +theme_bw(base_size = 20)+ theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+xlab("Model") + ylab("Total success proportion")+ scale_y_continuous(labels = scales::percent, limits = c(0,1))

plot_B <- ggplot(data = df2_T2[apply(bind_cols(df2_T2$Sample_size == 50, (df2_T2$Model %in% RSIHRModels)), 1, all),], aes(Model, Successes_total/Sample_size), width = 200, height = 200) + geom_violin(scale = "area") +theme_bw(base_size = 20)+ theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+xlab("Model") + ylab("Total success proportion")+ scale_y_continuous(labels = scales::percent, limits = c(0,1))

plot_C <- ggplot(data = df2_T2[apply(bind_cols(df2_T2$Sample_size == 50, (df2_T2$Model %in% RosenbergerModels)), 1, all),], aes(Model, Successes_total/Sample_size), width = 200, height = 200) + geom_violin(scale = "area") +theme_bw(base_size = 20)+ theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+xlab("Model") + ylab("Total success proportion")+ scale_y_continuous(labels = scales::percent, limits = c(0,1))

plot_D <- ggplot(data = df2_T2[apply(bind_cols(df2_T2$Sample_size == 50, (df2_T2$Model %in% OAModels)), 1, all),], aes(Model, Successes_total/Sample_size), width = 200, height = 200) + geom_violin(scale = "area") +theme_bw(base_size = 20)+ theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+xlab("Model") + ylab("Total success proportion")+ scale_y_continuous(labels = scales::percent, limits = c(0,1))

plot_E <- ggplot(data = df2_T2[apply(bind_cols(df2_T2$Sample_size == 50, (df2_T2$Model %in% GittinsModels)), 1, all),], aes(Model, Successes_total/Sample_size), width = 200, height = 200) + geom_violin(scale = "area") +theme_bw(base_size = 20)+ theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+xlab("Model") + ylab("Total success proportion")+ scale_y_continuous(labels = scales::percent, limits = c(0,1))

plot_F <- ggplot(data = df2_T2[apply(bind_cols(df2_T2$Sample_size == 50, (df2_T2$Model %in% MLModels)), 1, all),], aes(Model, Successes_total/Sample_size), width = 200, height = 200) + geom_violin(scale = "area") +theme_bw(base_size = 20)+ theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+xlab("Model") + ylab("Total success proportion")+ scale_y_continuous(labels = scales::percent, limits = c(0,1))
```

```{r}
plot_grid(plot_A, plot_B, plot_C, plot_D, plot_E, plot_F, ncol = 2, align = 'hv', labels = c("A", "B", "C", "D", "E", "F"))

ggsave(paste("C:/Users/richa/Desktop/Thesis/Images/Scenario_",scenarioNumber,"/Chart2_1_Combined_violins_SuccessComparison_n50_t2_Scenario_",scenarioNumber,".pdf", sep = ""), device = "pdf", width = 30, height = 50, units = "cm")
```

```{r}
plot_A <- ggplot(data = df2_T2[apply(bind_cols(df2_T2$Sample_size == 1000, (df2_T2$Model %in% NeymanModels)), 1, all),], aes(Model, Successes_total/Sample_size), width = 200, height = 200) + geom_violin(scale = "area") +theme_bw(base_size = 20)+ theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+xlab("Model") + ylab("Total success proportion")+ scale_y_continuous(labels = scales::percent, limits = c(0,1))

plot_B <- ggplot(data = df2_T2[apply(bind_cols(df2_T2$Sample_size == 1000, (df2_T2$Model %in% RSIHRModels)), 1, all),], aes(Model, Successes_total/Sample_size), width = 200, height = 200) + geom_violin(scale = "area") +theme_bw(base_size = 20)+ theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+xlab("Model") + ylab("Total success proportion")+ scale_y_continuous(labels = scales::percent, limits = c(0,1))

plot_C <- ggplot(data = df2_T2[apply(bind_cols(df2_T2$Sample_size == 1000, (df2_T2$Model %in% RosenbergerModels)), 1, all),], aes(Model, Successes_total/Sample_size), width = 200, height = 200) + geom_violin(scale = "area") +theme_bw(base_size = 20)+ theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+xlab("Model") + ylab("Total success proportion")+ scale_y_continuous(labels = scales::percent, limits = c(0,1))

plot_D <- ggplot(data = df2_T2[apply(bind_cols(df2_T2$Sample_size == 1000, (df2_T2$Model %in% OAModels)), 1, all),], aes(Model, Successes_total/Sample_size), width = 200, height = 200) + geom_violin(scale = "area") +theme_bw(base_size = 20)+ theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+xlab("Model") + ylab("Total success proportion")+ scale_y_continuous(labels = scales::percent, limits = c(0,1))

plot_E <- ggplot(data = df2_T2[apply(bind_cols(df2_T2$Sample_size == 1000, (df2_T2$Model %in% GittinsModels)), 1, all),], aes(Model, Successes_total/Sample_size), width = 200, height = 200) + geom_violin(scale = "area") +theme_bw(base_size = 20)+ theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+xlab("Model") + ylab("Total success proportion")+ scale_y_continuous(labels = scales::percent, limits = c(0,1))

plot_F <- ggplot(data = df2_T2[apply(bind_cols(df2_T2$Sample_size == 1000, (df2_T2$Model %in% MLModels)), 1, all),], aes(Model, Successes_total/Sample_size), width = 200, height = 200) + geom_violin(scale = "area") +theme_bw(base_size = 20)+ theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+xlab("Model") + ylab("Total success proportion")+ scale_y_continuous(labels = scales::percent, limits = c(0,1))
```

```{r}
plot_grid(plot_A, plot_B, plot_C, plot_D, plot_E, plot_F, ncol = 2, align = 'hv', labels = c("A", "B", "C", "D", "E", "F"))

ggsave(paste("C:/Users/richa/Desktop/Thesis/Images/Scenario_",scenarioNumber,"/Chart2_1_Combined_violins_SuccessComparison_n1000_t2_Scenario_",scenarioNumber,".pdf", sep = ""), device = "pdf",  width = 30, height = 50, units = "cm")
```


# Chart 3 - Average success proportion with sample size - T = 2

```{r}
labelMin = floor(min(df_summary_T2$averageSuccessProportion)*20)/20
labelMax = ceiling(max(df_summary_T2$averageSuccessProportion)*20)/20
```

```{r}
plot_A <- ggplot(data = df_summary_T2[df_summary_T2$Model %in% NeymanModels,], aes(Sample_size, averageSuccessProportion, color = Model), width = 200, height = 200) +geom_line()+xlab("Sample size") + ylab("Total success proprtion average")+ scale_y_continuous(labels = scales::percent, limits = c(labelMin, labelMax))
                                                                                                                                                                                                                               
plot_B <- ggplot(data = df_summary_T2[df_summary_T2$Model %in% RSIHRModels,], aes(Sample_size, averageSuccessProportion, color = Model), width = 200, height = 200) +geom_line()+xlab("Sample size") + ylab("Total success proprtion average")+ scale_y_continuous(labels = scales::percent, limits = c(labelMin, labelMax))

plot_C <- ggplot(data = df_summary_T2[df_summary_T2$Model %in% RosenbergerModels,], aes(Sample_size, averageSuccessProportion, color = Model), width = 200, height = 200) +geom_line()+xlab("Sample size") + ylab("Total success proprtion average")+ scale_y_continuous(labels = scales::percent, limits = c(labelMin, labelMax))

plot_D <- ggplot(data = df_summary_T2[df_summary_T2$Model %in% OAModels,], aes(Sample_size, averageSuccessProportion, color = Model), width = 200, height = 200) +geom_line()+xlab("Sample size") + ylab("Total success proprtion average")+ scale_y_continuous(labels = scales::percent, limits = c(labelMin, labelMax))

plot_E <- ggplot(data = df_summary_T2[df_summary_T2$Model %in% GittinsModels,], aes(Sample_size, averageSuccessProportion, color = Model), width = 200, height = 200) +geom_line()+xlab("Sample size") + ylab("Total success proprtion average")+ scale_y_continuous(labels = scales::percent, limits = c(labelMin, labelMax))

plot_F <- ggplot(data = df_summary_T2[df_summary_T2$Model %in% MLModels,], aes(Sample_size, averageSuccessProportion, color = Model), width = 200, height = 200) +geom_line()+xlab("Sample size") + ylab("Total success proprtion average")+ scale_y_continuous(labels = scales::percent, limits = c(labelMin, labelMax))
```

```{r}
plot_grid(plot_A, plot_B, plot_C, plot_D, plot_E, plot_F, ncol = 2, align = 'hv', labels = c("A", "B", "C", "D", "E", "F"))

ggsave(paste("C:/Users/richa/Desktop/Thesis/Images/Scenario_",scenarioNumber,"/Chart3_Combined_line_avgSuccessProp_t2_Scenario_",scenarioNumber,".pdf", sep = ""), device = "pdf", width = 40, height = 30, units = "cm")
```


# Chart 4 - Change in variance of total successes proportion with sample size - T = 2 
```{r}
labelMin = floor(min(df_summary_T2$averageAllocatedA)*20)/20
labelMax = ceiling(max(df_summary_T2$averageAllocatedA)*20)/20
```

```{r}
plot_A <- ggplot(data = df_summary_T2[df_summary_T2$Model %in% NeymanModels,], aes(Sample_size, averageAllocatedA, color = Model), width = 200, height = 200) +geom_line()+xlab("Sample size") + ylab("Average proprtion allocated to treatment A")+ scale_y_continuous(labels = scales::percent, limits = c(labelMin, labelMax))
                                                                                                                                                                                                                               
plot_B <- ggplot(data = df_summary_T2[df_summary_T2$Model %in% RSIHRModels,], aes(Sample_size, averageAllocatedA, color = Model), width = 200, height = 200) +geom_line()+xlab("Sample size") + ylab("Average proprtion allocated to treatment A")+ scale_y_continuous(labels = scales::percent, limits = c(labelMin, labelMax))

plot_C <- ggplot(data = df_summary_T2[df_summary_T2$Model %in% RosenbergerModels,], aes(Sample_size, averageAllocatedA, color = Model), width = 200, height = 200) +geom_line()+xlab("Sample size") + ylab("Average proprtion allocated to treatment A")+ scale_y_continuous(labels = scales::percent, limits = c(labelMin, labelMax))

plot_D <- ggplot(data = df_summary_T2[df_summary_T2$Model %in% OAModels,], aes(Sample_size, averageAllocatedA, color = Model), width = 200, height = 200) +geom_line()+xlab("Sample size") + ylab("Average proprtion allocated to treatment A")+ scale_y_continuous(labels = scales::percent, limits = c(labelMin, labelMax))

plot_E <- ggplot(data = df_summary_T2[df_summary_T2$Model %in% GittinsModels,], aes(Sample_size, averageAllocatedA, color = Model), width = 200, height = 200) +geom_line()+xlab("Sample size") + ylab("Average proprtion allocated to treatment A")+ scale_y_continuous(labels = scales::percent, limits = c(labelMin, labelMax))

plot_F <- ggplot(data = df_summary_T2[df_summary_T2$Model %in% MLModels,], aes(Sample_size, averageAllocatedA, color = Model), width = 200, height = 200) +geom_line()+xlab("Sample size") + ylab("Average proprtion allocated to treatment A")+ scale_y_continuous(labels = scales::percent, limits = c(labelMin, labelMax))
```

```{r}
plot_grid(plot_A, plot_B, plot_C, plot_D, plot_E, plot_F, ncol = 2, align = 'hv', labels = c("A", "B", "C", "D", "E", "F"))

ggsave(paste("C:/Users/richa/Desktop/Thesis/Images/Scenario_",scenarioNumber,"/Chart4_Combined_line_allocatedA_t2_Scenario_",scenarioNumber,".pdf", sep = ""), device = "pdf", width = 40, height = 30, units = "cm")
```


# Chart 5 Chi Sq power with sample size
## 1. Alpha = 0.05 
```{r}
labelMin = floor(min(df_summary_T2$ChiSq_005)*20)/20
labelMax = ceiling(max(df_summary_T2$ChiSq_005)*20)/20

ylabels = c("Power of Chi-Squared test (5% LoS)",
            "Power of Chi-Squared test (5% LoS)",
            "Type 1 error rate",
            "Power of Chi-Squared test (5% LoS)",
            "Type 1 error rate"
            )
ylabel = ylabels[as.numeric(scenarioNumber)]
```

```{r}
plot_A <- ggplot(data = df_summary_T2[df_summary_T2$Model %in% NeymanModels,], aes(Sample_size, ChiSq_005, color = Model), width = 200, height = 200) +geom_line()+xlab("Sample size") + 
  ylab(ylabel)+ scale_y_continuous(labels = scales::percent, limits = c(labelMin, labelMax))
                                                                                                                                                                                                                               
plot_B <- ggplot(data = df_summary_T2[df_summary_T2$Model %in% RSIHRModels,], aes(Sample_size, ChiSq_005, color = Model), width = 200, height = 200) +geom_line()+xlab("Sample size") + 
  ylab(ylabel)+ scale_y_continuous(labels = scales::percent, limits = c(labelMin, labelMax))

plot_C <- ggplot(data = df_summary_T2[df_summary_T2$Model %in% RosenbergerModels,], aes(Sample_size, ChiSq_005, color = Model), width = 200, height = 200) +geom_line()+xlab("Sample size") + 
 ylab(ylabel)+ scale_y_continuous(labels = scales::percent, limits = c(labelMin, labelMax))

plot_D <- ggplot(data = df_summary_T2[df_summary_T2$Model %in% OAModels,], aes(Sample_size, ChiSq_005, color = Model), width = 200, height = 200) +geom_line()+xlab("Sample size") + 
  ylab(ylabel)+ scale_y_continuous(labels = scales::percent, limits = c(labelMin, labelMax))

plot_E <- ggplot(data = df_summary_T2[df_summary_T2$Model %in% GittinsModels,], aes(Sample_size, ChiSq_005, color = Model), width = 200, height = 200) +geom_line()+xlab("Sample size") + 
  ylab(ylabel)+ scale_y_continuous(labels = scales::percent, limits = c(labelMin, labelMax))

plot_F <- ggplot(data = df_summary_T2[df_summary_T2$Model %in% MLModels,], aes(Sample_size, ChiSq_005, color = Model), width = 200, height = 200) +geom_line()+xlab("Sample size") + 
  ylab(ylabel)+ scale_y_continuous(labels = scales::percent, limits = c(labelMin, labelMax))
```

```{r}
plot_grid(plot_A, plot_B, plot_C, plot_D, plot_E, plot_F, ncol = 2, align = 'hv', labels = c("A", "B", "C", "D", "E", "F"))


ggsave(paste("C:/Users/richa/Desktop/Thesis/Images/Scenario_",scenarioNumber,"/Chart5_1_Combined_ChiSq_power_005_t2_Scenario_",scenarioNumber,".pdf", sep = ""), device = "pdf", width = 40, height = 30, units = "cm")
```



## 1. Alpha = 0.01
```{r}
labelMin = floor(min(df_summary_T2$ChiSq_001)*20)/20
labelMax = ceiling(max(df_summary_T2$ChiSq_001)*20)/20

ylabels = c("Power of Chi-Squared test (1% LoS)",
            "Power of Chi-Squared test (1% LoS)",
            "Type 1 error rate",
            "Power of Chi-Squared test (1% LoS)",
            "Type 1 error rate"
            )
ylabel = ylabels[as.numeric(scenarioNumber)]
```

```{r}
plot_A <- ggplot(data = df_summary_T2[df_summary_T2$Model %in% NeymanModels,], aes(Sample_size, ChiSq_001, color = Model), width = 200, height = 200) +geom_line()+xlab("Sample size") + 
  ylab(ylabel)+ scale_y_continuous(labels = scales::percent, limits = c(labelMin, labelMax))
                                                                                                                                                                                                                               
plot_B <- ggplot(data = df_summary_T2[df_summary_T2$Model %in% RSIHRModels,], aes(Sample_size, ChiSq_001, color = Model), width = 200, height = 200) +geom_line()+xlab("Sample size") + 
  ylab(ylabel)+ scale_y_continuous(labels = scales::percent, limits = c(labelMin, labelMax))

plot_C <- ggplot(data = df_summary_T2[df_summary_T2$Model %in% RosenbergerModels,], aes(Sample_size, ChiSq_001, color = Model), width = 200, height = 200) +geom_line()+xlab("Sample size") + 
 ylab(ylabel)+ scale_y_continuous(labels = scales::percent, limits = c(labelMin, labelMax))

plot_D <- ggplot(data = df_summary_T2[df_summary_T2$Model %in% OAModels,], aes(Sample_size, ChiSq_001, color = Model), width = 200, height = 200) +geom_line()+xlab("Sample size") + 
  ylab(ylabel)+ scale_y_continuous(labels = scales::percent, limits = c(labelMin, labelMax))

plot_E <- ggplot(data = df_summary_T2[df_summary_T2$Model %in% GittinsModels,], aes(Sample_size, ChiSq_001, color = Model), width = 200, height = 200) +geom_line()+xlab("Sample size") + 
  ylab(ylabel)+ scale_y_continuous(labels = scales::percent, limits = c(labelMin, labelMax))

plot_F <- ggplot(data = df_summary_T2[df_summary_T2$Model %in% MLModels,], aes(Sample_size, ChiSq_001, color = Model), width = 200, height = 200) +geom_line()+xlab("Sample size") + 
  ylab(ylabel)+ scale_y_continuous(labels = scales::percent, limits = c(labelMin, labelMax))
```

```{r}
plot_grid(plot_A, plot_B, plot_C, plot_D, plot_E, plot_F, ncol = 2, align = 'hv', labels = c("A", "B", "C", "D", "E", "F"))


ggsave(paste("C:/Users/richa/Desktop/Thesis/Images/Scenario_",scenarioNumber,"/Chart5_2_Combined_ChiSq_power_001_t2_Scenario_",scenarioNumber,".pdf", sep = ""), device = "pdf", width = 40, height = 30, units = "cm")
```



# Chart 6 Likelihood ratio test power with sample size
## 1. Alpha = 0.05 
```{r}
labelMin = floor(min(df_summary_T2$LR_test_005)*20)/20
labelMax = ceiling(max(df_summary_T2$LR_test_005)*20)/20

ylabels = c("Power of Likelihood ratio test (5% LoS)",
            "Power of Likelihood ratio test (5% LoS)",
            "Power of Likelihood ratio test (5% LoS)",
            "Power of Likelihood ratio test (5% LoS)",
            "Type 1 error rate"
            )
ylabel = ylabels[as.numeric(scenarioNumber)]
```

```{r}
plot_A <- ggplot(data = df_summary_T2[df_summary_T2$Model %in% NeymanModels,], aes(Sample_size, LR_test_005, color = Model), width = 200, height = 200) +geom_line()+xlab("Sample size") + 
  ylab(ylabel)+ scale_y_continuous(labels = scales::percent, limits = c(labelMin, labelMax))
                                                                                                                                                                                                                               
plot_B <- ggplot(data = df_summary_T2[df_summary_T2$Model %in% RSIHRModels,], aes(Sample_size, LR_test_005, color = Model), width = 200, height = 200) +geom_line()+xlab("Sample size") + 
  ylab(ylabel)+ scale_y_continuous(labels = scales::percent, limits = c(labelMin, labelMax))

plot_C <- ggplot(data = df_summary_T2[df_summary_T2$Model %in% RosenbergerModels,], aes(Sample_size, LR_test_005, color = Model), width = 200, height = 200) +geom_line()+xlab("Sample size") + 
 ylab(ylabel)+ scale_y_continuous(labels = scales::percent, limits = c(labelMin, labelMax))

plot_D <- ggplot(data = df_summary_T2[df_summary_T2$Model %in% OAModels,], aes(Sample_size, LR_test_005, color = Model), width = 200, height = 200) +geom_line()+xlab("Sample size") + 
  ylab(ylabel)+ scale_y_continuous(labels = scales::percent, limits = c(labelMin, labelMax))

plot_E <- ggplot(data = df_summary_T2[df_summary_T2$Model %in% GittinsModels,], aes(Sample_size, LR_test_005, color = Model), width = 200, height = 200) +geom_line()+xlab("Sample size") + 
  ylab(ylabel)+ scale_y_continuous(labels = scales::percent, limits = c(labelMin, labelMax))

plot_F <- ggplot(data = df_summary_T2[df_summary_T2$Model %in% MLModels,], aes(Sample_size, LR_test_005, color = Model), width = 200, height = 200) +geom_line()+xlab("Sample size") + 
  ylab(ylabel)+ scale_y_continuous(labels = scales::percent, limits = c(labelMin, labelMax))
```

```{r}
plot_grid(plot_A, plot_B, plot_C, plot_D, plot_E, plot_F, ncol = 2, align = 'hv', labels = c("A", "B", "C", "D", "E", "F"))

ggsave(paste("C:/Users/richa/Desktop/Thesis/Images/Scenario_",scenarioNumber,"/Chart6_1_Combined_LR_test_power_005_t2_Scenario_",scenarioNumber,".pdf", sep = ""), device = "pdf", width = 40, height = 30, units = "cm")
```



## 2. Alpha = 0.01
```{r}
labelMin = floor(min(df_summary_T2$LR_test_001)*20)/20
labelMax = ceiling(max(df_summary_T2$LR_test_001)*20)/20

ylabels = c("Power of Likelihood ratio test (1% LoS)",
            "Power of Likelihood ratio test (1% LoS)",
            "Power of Likelihood ratio test (1% LoS)",
            "Power of Likelihood ratio test (1% LoS)",
            "Type 1 error rate"
            )
ylabel = ylabels[as.numeric(scenarioNumber)]
```

```{r}
plot_A <- ggplot(data = df_summary_T2[df_summary_T2$Model %in% NeymanModels,], aes(Sample_size, LR_test_001, color = Model), width = 200, height = 200) +geom_line()+xlab("Sample size") + 
  ylab(ylabel)+ scale_y_continuous(labels = scales::percent, limits = c(labelMin, labelMax))
                                                                                                                                                                                                                               
plot_B <- ggplot(data = df_summary_T2[df_summary_T2$Model %in% RSIHRModels,], aes(Sample_size, LR_test_001, color = Model), width = 200, height = 200) +geom_line()+xlab("Sample size") + 
  ylab(ylabel)+ scale_y_continuous(labels = scales::percent, limits = c(labelMin, labelMax))

plot_C <- ggplot(data = df_summary_T2[df_summary_T2$Model %in% RosenbergerModels,], aes(Sample_size, LR_test_001, color = Model), width = 200, height = 200) +geom_line()+xlab("Sample size") + 
 ylab(ylabel)+ scale_y_continuous(labels = scales::percent, limits = c(labelMin, labelMax))

plot_D <- ggplot(data = df_summary_T2[df_summary_T2$Model %in% OAModels,], aes(Sample_size, LR_test_001, color = Model), width = 200, height = 200) +geom_line()+xlab("Sample size") + 
  ylab(ylabel)+ scale_y_continuous(labels = scales::percent, limits = c(labelMin, labelMax))

plot_E <- ggplot(data = df_summary_T2[df_summary_T2$Model %in% GittinsModels,], aes(Sample_size, LR_test_001, color = Model), width = 200, height = 200) +geom_line()+xlab("Sample size") + 
  ylab(ylabel)+ scale_y_continuous(labels = scales::percent, limits = c(labelMin, labelMax))

plot_F <- ggplot(data = df_summary_T2[df_summary_T2$Model %in% MLModels,], aes(Sample_size, LR_test_001, color = Model), width = 200, height = 200) +geom_line()+xlab("Sample size") + 
  ylab(ylabel)+ scale_y_continuous(labels = scales::percent, limits = c(labelMin, labelMax))
```

```{r}
plot_grid(plot_A, plot_B, plot_C, plot_D, plot_E, plot_F, ncol = 2, align = 'hv', labels = c("A", "B", "C", "D", "E", "F"))


ggsave(paste("C:/Users/richa/Desktop/Thesis/Images/Scenario_",scenarioNumber,"/Chart6_2_Combined_LR_test_power_001_t2_Scenario_",scenarioNumber,".pdf", sep = ""), device = "pdf", width = 40, height = 30, units = "cm")
```


# Chart 7 Scatter of power and average success
## n = 20
```{r}
ggplot(data = df_summary_T2[df_summary_T2$Sample_size == 30,], aes(x = averageSuccessProportion , y = ChiSq_005, color = Model, label = Model), width = 200) + geom_point() +xlab("Average total successes") + ylab("Power of ChiSq ar 5% Level of Signifcance")+ scale_y_continuous(labels = scales::percent) + scale_x_continuous(labels = scales::percent) + theme(legend.position = "none")
ggsave(paste("C:/Users/richa/Desktop/Thesis/Images/Scenario_",scenarioNumber,"/Chart7_a_Scatter_Power_Success_n20_t2_Scenario_",scenarioNumber,".pdf", sep = ""), device = "pdf", width = 15, units = "cm")
```

## n = 100
```{r}
ggplot(data = df_summary_T2[df_summary_T2$Sample_size == 100,], aes(x = averageSuccessProportion , y = ChiSq_005, color = Model), width = 200) + geom_point() +xlab("Average total successes") + ylab("Power of ChiSq ar 5% Level of Signifcance")+ scale_y_continuous(labels = scales::percent) + scale_x_continuous(labels = scales::percent) + theme(legend.position = "none")
ggsave(paste("C:/Users/richa/Desktop/Thesis/Images/Scenario_",scenarioNumber,"/Chart7_b_Scatter_Power_Success_n100_t2_Scenario_",scenarioNumber,".pdf", sep = ""), device = "pdf", width = 15, units = "cm")
```


# Chart 8: Distribution of percent of allocation A by sample size - T = 2 
```{r}
RA_RSIHR_Models = c("RA_Known_RSIHR", "RA_Estimated_RSIHR", "RA_DBCD_RSIHR")
labelMin_percA = floor(min(df2_T2[df2_T2$Model %in% RA_RSIHR_Models & df2_T2$Sample_size %% 100 == 0, "Perc_A"])*20)/20
labelMax_percA = ceiling(max(df2_T2[df2_T2$Model %in% RA_RSIHR_Models & df2_T2$Sample_size %% 100 == 0, "Perc_A"])*20)/20

labelMin_success = floor(min(df2_T2[df2_T2$Model %in% RA_RSIHR_Models & df2_T2$Sample_size %% 100 == 0, "AvgSuccess"])*20)/20
labelMax_success = ceiling(max(df2_T2[df2_T2$Model %in% RA_RSIHR_Models & df2_T2$Sample_size %% 100 == 0, "AvgSuccess"])*20)/20
```


```{r}
plot_A <- ggplot(data = df2_T2[df2_T2$Model == "RA_Known_RSIHR" & df2_T2$Sample_size %% 100 == 0,], aes(as.factor(Sample_size), Perc_A), width = 200) + geom_violin(scale = "area") +theme_bw(base_size = 20)+ theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+xlab("Sample size") + ylab("% allocated to treatment A")+ scale_y_continuous(labels = scales::percent, limits = c(labelMin_percA, labelMax_percA))

plot_C <- ggplot(data = df2_T2[df2_T2$Model == "RA_Estimated_RSIHR" & df2_T2$Sample_size %% 100 == 0,], aes(as.factor(Sample_size), Perc_A), width = 200) + geom_violin(scale = "area") +theme_bw(base_size = 20)+ theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+xlab("Sample size") + ylab("% allocated to treatment A")+ scale_y_continuous(labels = scales::percent, limits = c(labelMin_percA, labelMax_percA))

plot_E <- ggplot(data = df2_T2[df2_T2$Model == "RA_DBCD_RSIHR" & df2_T2$Sample_size %% 100 == 0,], aes(as.factor(Sample_size), Perc_A), width = 200) + geom_violin(scale = "area") +theme_bw(base_size = 20)+ theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+xlab("Sample size") + ylab("% allocated to treatment A")+ scale_y_continuous(labels = scales::percent, limits = c(labelMin_percA, labelMax_percA))

plot_B <- ggplot(data = df2_T2[df2_T2$Model == "RA_Known_RSIHR" & df2_T2$Sample_size %% 100 == 0,], aes(as.factor(Sample_size), Successes_total/Sample_size), width = 200) + geom_violin(scale = "area") +theme_bw(base_size = 20)+ theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+xlab("Sample size") + ylab("Success proportion")+ scale_y_continuous(labels = scales::percent, limits = c(labelMin_success, labelMax_success))

plot_D <- ggplot(data = df2_T2[df2_T2$Model == "RA_Estimated_RSIHR" & df2_T2$Sample_size %% 100 == 0,], aes(as.factor(Sample_size), Successes_total/Sample_size), width = 200) + geom_violin(scale = "area") +theme_bw(base_size = 20)+ theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+xlab("Sample size") + ylab("Success proportion")+ scale_y_continuous(labels = scales::percent, limits = c(labelMin_success, labelMax_success))

plot_F <- ggplot(data = df2_T2[df2_T2$Model == "RA_DBCD_RSIHR" & df2_T2$Sample_size %% 100 == 0,], aes(as.factor(Sample_size), Successes_total/Sample_size), width = 200) + geom_violin(scale = "area") +theme_bw(base_size = 20)+ theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+xlab("Sample size") + ylab("Success proportion")+ scale_y_continuous(labels = scales::percent, limits = c(labelMin_success, labelMax_success))

plot_grid(plot_A, plot_B, plot_C, plot_D, plot_E, plot_F, ncol = 2, align = 'hv', labels = c("A", "B", "C", "D", "E", "F"))

ggsave(paste("C:/Users/richa/Desktop/Thesis/Images/Scenario_",scenarioNumber,"/Chart8_Combined_Violins_successes_by_sample_size_t2_Scenario_",scenarioNumber,".pdf", sep = ""), device = "pdf", width = 40, height = 30, units = "cm")
```

## Alt plot - Sample size <100
```{r}
RA_RSIHR_Models = c("RA_Known_RSIHR", "RA_Estimated_RSIHR", "RA_DBCD_RSIHR")
labelMin_percA = floor(min(df2_T2[df2_T2$Model %in% RA_RSIHR_Models & df2_T2$Sample_size  <= 100, "Perc_A"])*20)/20
labelMax_percA = ceiling(max(df2_T2[df2_T2$Model %in% RA_RSIHR_Models & df2_T2$Sample_size <= 100, "Perc_A"])*20)/20

labelMin_success = floor(min(df2_T2[df2_T2$Model %in% RA_RSIHR_Models & df2_T2$Sample_size  <= 100, "AvgSuccess"])*20)/20
labelMax_success = ceiling(max(df2_T2[df2_T2$Model %in% RA_RSIHR_Models & df2_T2$Sample_size  <= 100, "AvgSuccess"])*20)/20
```


```{r}
plot_A <- ggplot(data = df2_T2[df2_T2$Model == "RA_Known_RSIHR" & df2_T2$Sample_size <= 100,], aes(as.factor(Sample_size), Perc_A), width = 200) + geom_violin(scale = "area") +theme_bw(base_size = 20)+ theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+xlab("Sample size") + ylab("% allocated to treatment A")+ scale_y_continuous(labels = scales::percent, limits = c(labelMin_percA, labelMax_percA))

plot_C <- ggplot(data = df2_T2[df2_T2$Model == "RA_Estimated_RSIHR" & df2_T2$Sample_size <= 100,], aes(as.factor(Sample_size), Perc_A), width = 200) + geom_violin(scale = "area") +theme_bw(base_size = 20)+ theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+xlab("Sample size") + ylab("% allocated to treatment A")+ scale_y_continuous(labels = scales::percent, limits = c(labelMin_percA, labelMax_percA))

plot_E <- ggplot(data = df2_T2[df2_T2$Model == "RA_DBCD_RSIHR" & df2_T2$Sample_size <= 100,], aes(as.factor(Sample_size), Perc_A), width = 200) + geom_violin(scale = "area") +theme_bw(base_size = 20)+ theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+xlab("Sample size") + ylab("% allocated to treatment A")+ scale_y_continuous(labels = scales::percent, limits = c(labelMin_percA, labelMax_percA))

plot_B <- ggplot(data = df2_T2[df2_T2$Model == "RA_Known_RSIHR" & df2_T2$Sample_size <= 100,], aes(as.factor(Sample_size), Successes_total/Sample_size), width = 200) + geom_violin(scale = "area") +theme_bw(base_size = 20)+ theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+xlab("Sample size") + ylab("Success proportion")+ scale_y_continuous(labels = scales::percent, limits = c(labelMin_success, labelMax_success))

plot_D <- ggplot(data = df2_T2[df2_T2$Model == "RA_Estimated_RSIHR" & df2_T2$Sample_size <= 100,], aes(as.factor(Sample_size), Successes_total/Sample_size), width = 200) + geom_violin(scale = "area") +theme_bw(base_size = 20)+ theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+xlab("Sample size") + ylab("Success proportion")+ scale_y_continuous(labels = scales::percent, limits = c(labelMin_success, labelMax_success))

plot_F <- ggplot(data = df2_T2[df2_T2$Model == "RA_DBCD_RSIHR" & df2_T2$Sample_size <= 100,], aes(as.factor(Sample_size), Successes_total/Sample_size), width = 200) + geom_violin(scale = "area") +theme_bw(base_size = 20)+ theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+xlab("Sample size") + ylab("Success proportion")+ scale_y_continuous(labels = scales::percent, limits = c(labelMin_success, labelMax_success))

plot_grid(plot_A, plot_B, plot_C, plot_D, plot_E, plot_F, ncol = 2, align = 'hv', labels = c("A", "B", "C", "D", "E", "F"))

ggsave(paste("C:/Users/richa/Desktop/Thesis/Images/Scenario_",scenarioNumber,"/Chart8_Combined_Alt_Violins_successes_by_sample_size_t2_Scenario_",scenarioNumber,".pdf", sep = ""), device = "pdf", width = 40, height = 30, units = "cm")
```





# Chart 9 - Change in variance of total successes proportion with sample size - T = 2
```{r}
ggplot(data =  df_summary_T2, aes(Sample_size, varSuccessProportion, color = Model)) +geom_line()+xlab("Sample size") + ylab("Variance of success proportion") + theme(legend.position="bottom")+ xlim(0, 250) + theme(legend.position = "none")
ggsave(paste("C:/Users/richa/Desktop/Thesis/Images/Scenario_",scenarioNumber,"/Chart9_all_line_varSuccessProp_t2_Scenario_",scenarioNumber,".pdf", sep = ""), device = "pdf", width = 40, height = 30, units = "cm")
```


```{r}
labelMin = floor(min(df_summary_T2$varSuccessProportion)*200)/200
labelMax = ceiling(max(df_summary_T2$varSuccessProportion)*200)/200
```


```{r}
plot_A <- ggplot(data =  df_summary_T2[(df_summary_T2$Model %in% NeymanModels) & df_summary_T2$Sample_size <=1000,], aes(Sample_size, varSuccessProportion, color = Model)) +geom_line()+xlab("Sample size") + ylab("Variance of success proportion") + theme(legend.position="bottom")+ xlim(0, 1000) + ylim(labelMin, labelMax)

plot_B <- ggplot(data =  df_summary_T2[(df_summary_T2$Model %in% RSIHRModels) & df_summary_T2$Sample_size <=1000,], aes(Sample_size, varSuccessProportion, color = Model)) +geom_line()+xlab("Sample size") + ylab("Variance of success proportion") + theme(legend.position="bottom")+ xlim(0, 1000)+ ylim(labelMin, labelMax)

plot_C <- ggplot(data =  df_summary_T2[(df_summary_T2$Model %in% RosenbergerModels) & df_summary_T2$Sample_size <=1000,], aes(Sample_size, varSuccessProportion, color = Model)) +geom_line()+xlab("Sample size") + ylab("Variance of success proportion") + theme(legend.position="bottom")+ xlim(0, 1000)+ ylim(labelMin, labelMax)

plot_D <- ggplot(data =  df_summary_T2[(df_summary_T2$Model %in% OAModels) & df_summary_T2$Sample_size <=1000,], aes(Sample_size, varSuccessProportion, color = Model)) +geom_line()+xlab("Sample size") + ylab("Variance of success proportion") + theme(legend.position="bottom")+ xlim(0, 1000)+ ylim(labelMin, labelMax)

plot_E <- ggplot(data =  df_summary_T2[(df_summary_T2$Model %in% GittinsModels) & df_summary_T2$Sample_size <=1000,], aes(Sample_size, varSuccessProportion, color = Model)) +geom_line()+xlab("Sample size") + ylab("Variance of success proportion") + theme(legend.position="bottom")+ xlim(0, 1000)+ ylim(labelMin, labelMax)

plot_F <- ggplot(data =  df_summary_T2[(df_summary_T2$Model %in% MLModels) & df_summary_T2$Sample_size <=1000,], aes(Sample_size, varSuccessProportion, color = Model)) +geom_line()+xlab("Sample size") + ylab("Variance of success proportion") + theme(legend.position="bottom")+ xlim(0, 1000)+ ylim(labelMin, labelMax)

plot_grid(plot_A, plot_B, plot_C, plot_D, plot_E, plot_F, ncol = 2, align = 'hv', labels = c("A", "B", "C", "D", "E", "F"))


ggsave(paste("C:/Users/richa/Desktop/Thesis/Images/Scenario_",scenarioNumber,"/Chart9_Combined_line_varSuccessProp_t2_Scenario_",scenarioNumber,".pdf", sep = ""), device = "pdf", width = 40, height = 30, units = "cm")
```








