---
title: "R Notebook"
output:
  pdf_document: default
  html_notebook: default
---

# Allocation methods
Let us start by defining functions for each allocation method

## Allocation methods that don't take into account covariates

### Random and Restricted randomisation

```{r}

## Allocation functions that don't take into account covariates
source("./Models/Simple/1_RandomAllocation.r")
source("./Models/Simple/2_NeymanKnown.r")
source("./Models/Simple/3_RSIHRKnown.r")
source("./Models/Simple/4_RosenbergerKnown.r")
source("./Models/Simple/5_OptimalAdjustedKnown.r")
source("./Models/Simple/6_biasedCoin.r")
```

## Response adaptive randomisation

### Coin based designs
```{r}
source("./Models/RA/7_DoublyBiasedCoin.r")

```


### Turn based and Gittins index
```{r}
source("./Models/RA/8_PlayTheWinner.R")
source("./Models/RA/9_PlayTheWinnerRandomised_2T.R")
source("./Models/RA/10_PlayTheWinnerRandomised.R") # Not working yet
source("./Models/RA/11_gittinsIndex.R") # Not working yet


```

### Sequential estimation techniques Two Treatments
```{r}
source("./Models/RA/12_NeymanEstimated_binary.R")
source("./Models/RA/13_RSIHR_binary.R")
source("./Models/RA/14_Rosenberger_binary.R")
source("./Models/RA/15_OptimalAdjusted_binary.R")
```

### Sequential estimation techniques Multiple Treatments - simple extensions
```{r}
source("./Models/RA/16_NeymanEstimated_Multiple.R")
source("./Models/RA/17_RSIHREstimated_multiple.R")
source("./Models/RA/18_Rosenberger_multiple.R")
source("./Models/RA/19_OptimalAdjusted_multiple.R")

```


## Allocation strategies that take into account covariates

### Sequential estimation
```{r}

## Allocation functions that take into account covariates
CARA1 <- function(n, n0, T, Z, Results){
  
}

CARA2 <- function(n, n0, T, Z, Results){
  
}

CARA3 <- function(n, n0, T, Z, Results){
  
}

```




# Simulation
setting up the problem

```{r}
n = 1000 # Number of subjects
n0 = 5

Z = rbinom(n,1,0.5) # Simulate single binary covariate

SuccessProbs = c(0.2, 0.6)

SuccessProbs_Z = matrix(data = c(0.1, 0.3, 0.7, 0.1), nrow = 2, ncol = 2)
```

Now we can model different treatment allocation strategies

```{r}
# Results
T = length(SuccessProbs)
Results = matrix(0, nrow = n, ncol = T)

for (i in 1:T) {
  Results[ , i] = rbinom(n, 1, SuccessProbs[i]) 
}

# Results measures
source("./ResultMeasures/successCount.R")

library(pwr)


# Pure random
Allocation_random = randomAllocation(n, T)
TotalSuccesses_Random = successCount(Allocation_random, Results)

h = SuccessProbs[2] - SuccessProbs[1]
n1 = sum(Allocation_random == 1)
n2 = n - n1
power = pwr.2p2n.test(h = h, n1 =  n1, n2 = n2, sig.level=0.05, alternative = "two.sided")

  
# Biased Coin
Allocation_biasedCoin = biasedCoinAllocation(n, 1/3)
TotalSuccesses_biasedCoin = successCount(Allocation_biasedCoin[,1], Results)

```

```{r}
# Play the winner
Allocation_playTheWinner = playTheWinner(n, T, Results)
TotalSuccesses_playTheWinner = successCount(Allocation_playTheWinner, Results)

Allocation_playTheWinner_Randomised = playTheWinnerRandomised_2T(n, Results, 1, 1)
TotalSuccesses_playTheWinner_Randomised = successCount(Allocation_playTheWinner_Randomised[,1], Results)

# Neyman Allocations
Allocation_neyamn_known = neymanKnown(n, T, Results, SuccessProbs)
TotalSuccesses_neyamn_known = successCount(Allocation_neyamn_known, Results)

Allocation_neyamn_estimated = neymanEstimated_binary(n, n0, Results)
TotalSuccesses_neyamn_estimated = successCount(Allocation_neyamn_estimated, Results)

Allocation_RSHIR_binary = RSIHR_binary(n, n0, Results)
TotalSuccesses_RSHIR_binary = successCount(Allocation_RSHIR_binary, Results)

Allocation_Rosenberger_binary =Rosenberger_binary(n, n0, Results)
TotalSuccesses_Rosenberger_binary = successCount(Allocation_Rosenberger_binary, Results)

Allocation_OptimalAdjusted_binary = OptimalAdjusted_binary(n, n0, Results)
TotalSuccesses_OptimalAdjusted_binary = successCount(Allocation_OptimalAdjusted_binary, Results)
```

```{r}
table(Allocation_random)
table(Allocation_biasedCoin[,1])
table(Allocation_playTheWinner)
table(Allocation_neyamn_known)
table(Allocation_neyamn_estimated)
table(Allocation_RSHIR_binary)
table(Allocation_Rosenberger_binary)
table(Allocation_OptimalAdjusted_binary)

TotalSuccesses_Random
TotalSuccesses_biasedCoin
TotalSuccesses_playTheWinner
TotalSuccesses_playTheWinner_Randomised
TotalSuccesses_neyamn_known
TotalSuccesses_neyamn_estimated
TotalSuccesses_RSHIR_binary
TotalSuccesses_Rosenberger_binary
TotalSuccesses_OptimalAdjusted_binary

```



setting up multi-treatment the problem

```{r}
n = 1000 # Number of subjects
n0 = 5

Z = rbinom(n,1,0.5) # Simulate single binary covariate

SuccessProbs = c(0.2, 0.6, 0.8, 0.5, 0.2)

SuccessProbs_Z = matrix(data = c(0.1, 0.3, 0.7, 0.1, 0.8, 0.8, 0.2, 0.8, 0.15, 0.25), nrow = 5, ncol = 2)

T = 5
```

