---
title: "V4_Creation of charts"
author: "Richard Alessi"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(dplyr)
library(ggplot2)
library(tibble)

library(foreach)
library(parallel)
library(iterators)
library(doParallel)
```




## Read in values
```{r}
df2_T5 = readRDS("C:/Users/richa/Desktop/Thesis/V2_Results/df2_T5.RDS")
df2_T2 = readRDS("C:/Users/richa/Desktop/Thesis/V2_Results/df2_T2.RDS")
```



# Chart 1: Distribution of percent of allocation A by sample size - T = 2 

```{r}
ggplot(data = df2_T2[df2_T2$Model == "RA_DBCD_RSIHR",], aes(as.factor(Sample_size), Perc_A), width = 200) + geom_violin(scale = "area") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+xlab("Sample size") + ylab("% allocated to treatment A")+ scale_y_continuous(labels = scales::percent)
ggsave(paste("C:/Users/richa/Desktop/Thesis/Images/Chart1_violins_percA_by_sample_size_RA_DBCD_RSIHR_t2_",format(Sys.time(), "%Y%m%d"),".pdf", sep = ""), device = "pdf", width = 15, units = "cm")
```



# Chart 1a: Distribution of percent of allocation A by sample size - T = 5

```{r}
ggplot(data = df2_T5[df2_T5$Model == "RA_DBCD_RSIHR",], aes(as.factor(Sample_size), Perc_A), width = 200) + geom_violin(scale = "area") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+xlab("Sample size") + ylab("% allocated to treatment A")+ scale_y_continuous(labels = scales::percent)
ggsave(paste("C:/Users/richa/Desktop/Thesis/Images/Chart1a_violins_percA_by_sample_size_RA_DBCD_RSIHR_t5_",format(Sys.time(), "%Y%m%d"),".pdf", sep = ""), device = "pdf", width = 15, units = "cm")
```


# Chart 2 - Percent allocated to A, all model violins, t = 2, n = 100


```{r}
ggplot(data = df2_T2[df2_T2$Sample_size == 100,], aes(Model, Perc_A), width = 200) + geom_violin(scale = "area") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+xlab("Model") + ylab("% allocated to treatment A")+ scale_y_continuous(labels = scales::percent)
ggsave(paste("C:/Users/richa/Desktop/Thesis/Images/Chart2_violins_percA_n100_t2_",format(Sys.time(), "%Y%m%d"),".pdf", sep = ""), device = "pdf", width = 15, units = "cm")
```
# Chart 3 - Percent allocated to A, all model violins, t = 2, n = 1000

```{r}
ggplot(data = df2_T2[df2_T2$Sample_size == 1000,], aes(Model, Perc_A), width = 200) + geom_violin(scale = "area") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+xlab("Model") + ylab("% allocated to treatment A")+ scale_y_continuous(labels = scales::percent)
ggsave(paste("C:/Users/richa/Desktop/Thesis/Images/Chart3_violins_percA_n1000_t2_",format(Sys.time(), "%Y%m%d"),".pdf", sep = ""), device = "pdf", width = 15, units = "cm")
```

# Chart 4 - Percent allocated to A, all model violins, t = 5, n = 100


```{r}
ggplot(data = df2_T5[df2_T5$Sample_size == 100,], aes(Model, Perc_A), width = 200) + geom_violin(scale = "area") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+xlab("Model") + ylab("% allocated to treatment A")+ scale_y_continuous(labels = scales::percent)
ggsave(paste("C:/Users/richa/Desktop/Thesis/Images/Chart4_violins_percA_n100_t5_",format(Sys.time(), "%Y%m%d"),".pdf", sep = ""), device = "pdf", width = 15, units = "cm")
```
# Chart 5 - Percent allocated to A, all model violins, t = 5, n = 1000

```{r}
ggplot(data = df2_T5[df2_T5$Sample_size == 1000,], aes(Model, Perc_A), width = 200) + geom_violin(scale = "area") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+xlab("Model") + ylab("% allocated to treatment A")+ scale_y_continuous(labels = scales::percent)
ggsave(paste("C:/Users/richa/Desktop/Thesis/Images/Chart5_violins_percA_n1000_t5_",format(Sys.time(), "%Y%m%d"),".pdf", sep = ""), device = "pdf", width = 15, units = "cm")
```


# Chart 6 - Tables of key values
```{r}
n_s = unique(df2_T2$Sample_Size)
models = unique(df2_T2$Model)
df_summary_T2 = data.frame(Sample_size = integer(), Model = character() , averageSuccessProportion = numeric(), varianceSuccessProportion = numeric(), averageAllocatedA = numeric(), varianceAllocatedA = numeric(), averagePower= numeric() )

df_summary_T2 <- df2_T2 %>% group_by(Model, Sample_size) %>% summarise(averageSuccessProportion = mean(Successes_total/Sample_size), varSuccessProportion = var(Successes_total/Sample_size), averageAllocatedA = mean(Perc_A/Sample_size), VarAllocatedA = var(Perc_A/Sample_size), averagePower = mean(Power), varPower = var(Power))

df_summary_T2
```

```{r}
n_s = unique(df2_T5$Sample_Size)
models = unique(df2_T5$Model)
df_summary_T5 = data.frame(Sample_size = integer(), Model = character() , averageSuccessProportion = numeric(), varianceSuccessProportion = numeric(), averageAllocatedA = numeric(), varianceAllocatedA = numeric(), averagePower= numeric() )

df_summary_T5 <- df2_T5 %>% group_by(Model, Sample_size) %>% summarise(averageSuccessProportion = mean(Successes_total/Sample_size), varSuccessProportion = var(Successes_total/Sample_size), averageAllocatedA = mean(Perc_A/Sample_size), VarAllocatedA = var(Perc_A/Sample_size), averagePower = mean(Power), varPower = var(Power))

df_summary_T5
```



# Chart 7 - Change in variance of total successes proportion with sample size - T = 2
```{r}
RosenbergerModels = c("RA_Known_Rosenberger", "CARA_Known_Rosenberger", "RA_Estimated_Rosenberger", "CARA_Estimated_Rosenberger", "RA_DBCD_Rosenberger", "CARA_DBCD_Rosenberger")
ggplot(data =  df_summary_T2[(df_summary_T2$Model %in% NeymanModels),], aes(Sample_size, varSuccessProportion, color = Model)) +geom_line()+xlab("Sample size") + ylab("Variance of success proportion") + theme(legend.position="bottom")+ xlim(40, 1000)

ggsave(paste("C:/Users/richa/Desktop/Thesis/Images/Chart7_line_varSuccessProp_t2_",format(Sys.time(), "%Y%m%d"),".pdf", sep = ""), device = "pdf", width = 15, units = "cm")
```



# Chart 8 - Change in variance of total successes proportion with sample size - T = 5
```{r}
ggplot(data = df_summary_T5, aes(Sample_size, averageSuccessProportion, color = Model)) +geom_line()+xlab("Sample size") + ylab("Total success proprtion average")+ scale_y_continuous(labels = scales::percent)

ggsave(paste("C:/Users/richa/Desktop/Thesis/Images/Chart8_line_avgSuccessProp_t5_",format(Sys.time(), "%Y%m%d"),".pdf", sep = ""), device = "pdf", width = 7, units = "cm")

```


# Chart 9 - Comparison of RA and CARA for Neyman - T = 2, n = 100
```{r}
NeymanModels = c("RA_Known_Neyman", "CARA_Known_Neyman", "RA_Estimated_Neyman", "CARA_Estimated_Neyman", "RA_DBCD_Neyman", "CARA_DBCD_Neyman")
ggplot(data = df2_T5[apply(bind_cols(df2_T5$Sample_size == 100, (df2_T5$Model %in% NeymanModels)), 1, all),], aes(Model, Successes_total/Sample_size), width = 200) + geom_violin(scale = "area") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+xlab("Model") + ylab("Total success proportion")+ scale_y_continuous(labels = scales::percent)

ggsave(paste("C:/Users/richa/Desktop/Thesis/Images/Chart9_violins_SuccessNeymanComparison_n100_t2_",format(Sys.time(), "%Y%m%d"),".pdf", sep = ""), device = "pdf", width = 15, units = "cm")
```

# Chart 10 - Comparison of RA and CARA for RSIHR - T = 2, n = 100
```{r}
RSIHRModels = c("RA_Known_RSIHR", "CARA_Known_RSIHR", "RA_Estimated_RSIHR", "CARA_Estimated_RSIHR", "RA_DBCD_RSIHR", "CARA_DBCD_RSIHR")
ggplot(data = df2_T5[apply(bind_cols(df2_T5$Sample_size == 100, (df2_T5$Model %in% RSIHRModels)), 1, all),], aes(Model, Successes_total/Sample_size), width = 200) + geom_violin(scale = "area") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+xlab("Model") + ylab("Total success proportion")+ scale_y_continuous(labels = scales::percent)

ggsave(paste("C:/Users/richa/Desktop/Thesis/Images/Chart10_violins_SuccessRSIHRComparison_n100_t2_",format(Sys.time(), "%Y%m%d"),".pdf", sep = ""), device = "pdf", width = 15, units = "cm")
```


# Chart 11 - Comparison of RA and CARA for Rosenberger - T = 2, n = 100
```{r}
RosenbergerModels = c("RA_Known_Rosenberger", "CARA_Known_Rosenberger", "RA_Estimated_Rosenberger", "CARA_Estimated_Rosenberger", "RA_DBCD_Rosenberger", "CARA_DBCD_Rosenberger")
ggplot(data = df2_T5[apply(bind_cols(df2_T5$Sample_size == 100, (df2_T5$Model %in% RosenbergerModels)), 1, all),], aes(Model, Successes_total/Sample_size), width = 200) + geom_violin(scale = "area") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+xlab("Model") + ylab("Total success proportion")+ scale_y_continuous(labels = scales::percent)

ggsave(paste("C:/Users/richa/Desktop/Thesis/Images/Chart11_violins_SuccessRosenbergerComparison_n100_t2_",format(Sys.time(), "%Y%m%d"),".pdf", sep = ""), device = "pdf", width = 15, units = "cm")
```


# Chart 12 - Comparison of RA and CARA for Optimally Adjusted - T = 2, n = 100
```{r}
OptimallyAdjustedModels = c("RA_Known_OptimallyAdjusted", "CARA_Known_OptimallyAdjusted", "RA_Estimated_OptimallyAdjusted", "CARA_Estimated_OptimallyAdjusted", "RA_DBCD_OptimallyAdjusted", "CARA_DBCD_OptimallyAdjusted")
ggplot(data = df2_T5[apply(bind_cols(df2_T5$Sample_size == 100, (df2_T5$Model %in% OptimallyAdjustedModels)), 1, all),], aes(Model, Successes_total/Sample_size), width = 200) + geom_violin(scale = "area") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+xlab("Model") + ylab("Total success proportion")+ scale_y_continuous(labels = scales::percent)

ggsave(paste("C:/Users/richa/Desktop/Thesis/Images/Chart12_violins_SuccessOptimallyAdjustedComparison_n100_t2_",format(Sys.time(), "%Y%m%d"),".pdf", sep = ""), device = "pdf", width = 15, units = "cm")
```



# Chart 13 - Violins of all models - success totals n =100, t = 2

```{r}
ggplot(data = df2_T2[df2_T2$Sample_size == 100,], aes(Model, Successes_total/Sample_size), width = 2000) + geom_violin(scale = "area") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+xlab("Model") + ylab("Total success proprtion")+ scale_y_continuous(labels = scales::percent)

ggsave(paste("C:/Users/richa/Desktop/Thesis/Images/Chart13_violins_successes_n100_t2_",format(Sys.time(), "%Y%m%d"),".pdf", sep = ""), device = "pdf", width = 15, units = "cm")
```


# Chart 14 - Violins of all models - success totals n =1000, t = 2

```{r}
ggplot(data = df2_T2[df2_T2$Sample_size == 1000,], aes(Model, Successes_total/Sample_size), width = 2000) + geom_violin(scale = "area") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+xlab("Model") + ylab("Total success proprtion")+ scale_y_continuous(labels = scales::percent)

ggsave(paste("C:/Users/richa/Desktop/Thesis/Images/Chart14_violins_successes_n1000_t2_",format(Sys.time(), "%Y%m%d"),".pdf", sep = ""), device = "pdf", width = 15, units = "cm")
```


# Chart 15 - Violins of all models - success totals n =100, t = 5

```{r}
ggplot(data = df2_T5[df2_T5$Sample_size == 100,], aes(Model, Successes_total/Sample_size), width = 2000) + geom_violin(scale = "area") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+xlab("Model") + ylab("Total success proprtion")+ scale_y_continuous(labels = scales::percent)

ggsave(paste("C:/Users/richa/Desktop/Thesis/Images/Chart15_violins_successes_n100_t_",format(Sys.time(), "%Y%m%d"),".pdf", sep = ""), device = "pdf", width = 15, units = "cm")
```


# Chart 16 - Violins of all models - success totals n =1000, t = 5

```{r}
ggplot(data = df2_T5[df2_T5$Sample_size == 1000,], aes(Model, Successes_total/Sample_size), width = 2000) + geom_violin(scale = "area") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+xlab("Model") + ylab("Total success proprtion")+ scale_y_continuous(labels = scales::percent)

ggsave(paste("C:/Users/richa/Desktop/Thesis/Images/Chart16_violins_successes_n1000_t5_",format(Sys.time(), "%Y%m%d"),".pdf", sep = ""), device = "pdf", width = 15, units = "cm")
```



# Chart 17 - Stack bars of treatment allocations, t = 5, n = 100

```{r}
df2_T5_Perc_A = df2_T5 %>% select(Model, Sample_size, A, B, C, D, E)
df_flat_T5 <- df2_T5_Perc_A %>% pivot_longer(cols = A:E, values_to = "mean") 
ggplot(data = df_flat_T5[df_flat_T5$Sample_size == 100,], aes(x = Model, y = mean, fill = name), width = 2000) +  geom_bar(position="stack", stat="identity") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+xlab("Model") + ylab("Allocation breakdown")+ scale_y_continuous(labels = scales::percent)

ggsave(paste("C:/Users/richa/Desktop/Thesis/Images/Chart17_stacks_PercA_n100_t5_",format(Sys.time(), "%Y%m%d"),".pdf", sep = ""), device = "pdf", width = 15, units = "cm")
```


# Chart 18 - Stack bars of treatment allocations, t = 5, n = 1000

```{r}
ggplot(data = df_flat_T5[df_flat_T5$Sample_size == 1000,], aes(x = Model, y = mean, fill = name), width = 2000) +  geom_bar(position="stack", stat="identity") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+xlab("Model") + ylab("Allocation breakdown")+ scale_y_continuous(labels = scales::percent)

ggsave(paste("C:/Users/richa/Desktop/Thesis/Images/Chart18_stacks_PercA_n1000_t5_",format(Sys.time(), "%Y%m%d"),".pdf", sep = ""), device = "pdf", width = 15, units = "cm")
```

